\documentclass{article}
\usepackage{amsmath}

\begin{document}

\section{Methods}

\subsection{Numerical Integration and Topological Enforcement}

The field $\phi(\mathbf{x},t)$ obeys the damped Klein-Gordon equation with a quartic gradient stabilizer,
\begin{equation}
\ddot{\phi} + \gamma \dot{\phi} - \nabla^2 \phi + 4\lambda \phi (\phi^2 - 1) + \frac{\beta}{2} \nabla^2 (|\nabla \phi|^2) = 0.
\end{equation}
Spatial derivatives are computed pseudo-spectrally: the field is Fourier transformed, multiplied by $-k^2$ (Laplacian) or $\mathrm{i}\mathbf{k}$ (gradient), and inverse-transformed. The nonlinear $\beta$-term is evaluated in real space after spectral gradients, ensuring alias-free accuracy. Time integration uses leap-frog with $\Delta t = 10^{-3}$ s, satisfying the Courant condition.

Topological winding is preserved by a projection operator: after each update, the net phase change along the central line is measured, rounded to the nearest integer, and corrected with a linear phase shift. This enforces exact integer winding with drift $<10^{-8}$ over $>10^4$ steps.

For 256$^3$ grids, domain decomposition into four z-slabs ($\sim$16 GB each) enables single-GPU execution. Slab boundaries are averaged for periodicity, with global projection applied post-stitch.

\subsection{Gravitational-Wave Post-Processing}

Quadrupole radiation from energy loss gives strain
\begin{equation}
h(t) = \frac{2G}{c^4 R} \beta E_0 r_c^2 e^{-\gamma_{\rm eff} t} \sin(2\pi f_0 t),
\end{equation}
with $r_c = \sqrt{\beta / E_1}$, $f_0 = 30$ Hz, $R = 40$ Mpc. PSD follows $S_h(f) \propto f^{-2}$, matching LVK O4 bursts.

\end{document}
